\documentclass[journal]{IEEEtran}


\usepackage{graphicx,subcaption} % figure related
\usepackage{amsfonts,amssymb,amsmath,amsthm,amsopn}	% math related
\usepackage{hhline,booktabs,colortbl,multirow,tabularx,diagbox,threeparttable} % table related
\usepackage[listings,skins,breakable]{tcolorbox}
\usepackage[ruled, vlined, linesnumbered, commentsnumbered]{algorithm2e}

\usepackage{enumerate}
\usepackage{authblk}
\usepackage{footnote}
\usepackage{hyperref}
\usepackage{prettyref}
\usepackage{cite}
\usepackage{setspace}
\usepackage{color}
\usepackage{xcolor}  % Required for custom colors

\usepackage{relsize}

\usepackage{pgfplots}
\usepackage{tikz}

\SetKwFor{Parallel}{for each}{do in parallel}{end for}
\SetKw{Of}{of}

% \def\hlinew#1{%
%   \noalign{\ifnum0=`}\fi\hrule \@height #1 \futurelet
%    \reserved@a\@xhline}
% \makeatother

% \definecolor{mycyan}{gray}{.7}

\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{property}{Property}

% \let\oldnl\nl% Store \nl in \oldnl
% \newcommand{\noln}{\renewcommand{\nl}{\let\nl\oldnl}}

% correct bad hyphenation here
% \hyphenation{op-tical net-works semi-conduc-tor}

% \newcommand\notealf[1]{\mbox{}\marginpar{\footnotesize\raggedright\hspace{0pt}\color{blue}\emph{#1}}}
\newcommand{\pref}{\prettyref}

\newrefformat{fig}{Fig.~\ref{#1}}
\newrefformat{tbl}{Table~\ref{#1}}
\newrefformat{sec}{Section~\ref{#1}}
\newrefformat{app}{Appendix~\ref{#1}}
\newrefformat{alg}{Algorithm~\ref{#1}}
\newrefformat{property}{Property~\ref{#1}}
\newrefformat{theorem}{Theorem~\ref{#1}}
\newrefformat{corollary}{Corollary~\ref{#1}}
\newrefformat{proposition}{Proposition~\ref{#1}}
\newrefformat{def}{Definition~\ref{#1}}
\newrefformat{eq}{equation~(\ref{#1})}

% \captionsetup{compatibility=false}

\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{P}[1]{>{\raggedright\arraybackslash}p{#1}}

\newcommand{\abs}[1]{\left\lvert #1 \right\rvert}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}

% \makeatletter
% \def\BState{\State\hskip-\ALG@thistlm}
% \makeatother

% \setlength{\belowcaptionskip}{-1em}
	
\begin{document}

\title{Routing-Led Algorithm for Large-Scale VNF Placement Problems}

\author{
	Joseph Billingsley,~\IEEEmembership{Student Member,~IEEE},
	Ke Li,~\IEEEmembership{Member,~IEEE},
	Wang Miao,
	Geyong Min,
	Nektarios Georgalas
	\thanks{J. Billingsley, K. Li, W. Miao and G. Min are with the Department of Computer Science, University of Exeter, North Park Road, Exeter, EX4 4QF, UK (e-mail: \{j.billingsley, k.li, wang.miao, g.min\}@exeter.ac.uk)}
	\thanks{N. Georgalas is with the Research and Innovation, British Telecom, Martlesham, UK (e-mail: nektarios.georgalas@bt.com)}
}

\maketitle

\begin{abstract}
	Modern data centers contain thousands of servers making them major consumers of electricity. To minimize their environmental impact, it is critical that we use their resources efficiently. In this paper we study how to discover the optimal placement of virtual network functions in large scale data centers. We propose a novel parallel metaheuristic, fast heuristic objective functions of the QoS and new memory efficient data structures for large networks. We further identify a simple, fast heuristic that can produce competitive solutions to very large problem instances. Using these new concepts, we are able to find high quality solutions for data centres with up to 64,000 servers.
\end{abstract}

\begin{IEEEkeywords}
	Network Function Virtualization, Multi-Objective Optimization, Routing-Led VNF Placement.
\end{IEEEkeywords}

% TODO: 
%		Standardize notations

\input{introduction}

\input{literature_review}

\input{problem_formulation}

\input{optimisation}

\input{objective_functions}

\input{performance_evaluation}

\input{conclusions}

\section*{Acknowledgment}
K. Li was supported by UKRI Future Leaders Fellowship (Grant No. MR/S017062/1) and Royal Society (Grant No. IEC/NSFC/170243). J. Billingsley was supported by EPSRC Industrial CASE and British Telecom (Grant No. 16000177).

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv, bibliography}

\end{document}